Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-06-26 docs/mvfits_paper/mvf.tex
updating docs

    \State Calculate the model representation error, e.g.: $\epsilon = |var(\hatU \vecmu - \vec{f})|/var(\vec{f})$, where $var$ is the variance of the respective list.

@@

    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.

@@

      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
      \State $done = |\epsilon^{(n)}-\epsilon^{(n-1)}| < tol$
      \State Implicitly, $n = n+1$

@@

\par We present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.

@@

@@

>>>>

    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $var$ is the variance of the respective list.

@@

    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.

@@

      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
      \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
      \State (Implicitly, $n = n+1$)

@@

\par We briefly review the application of \gmvr{} to a toy problem.
% Cross validation and removal of the last added basis symbol are used to assess model accuracy.
We then present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.

@@

\subsection{\gmvr{} Toy Problem}
Here

@@

    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
	\caption{ Fractional residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
  \label{fig:qnm_err}
